Parsing Postfix log files

### 2009-04-06 doc/logparser-results.tex
Consistent float placement.
Added graphs showing parsing time of perfect best and worst vs optimal and reverse orderings. Started writing about perfect best and worst, but didn't get it finished.

\begin{table}[htbp]
    \caption{Details of the computer used to generate statistics}
    \empty{}\label{Details of the computer used to generate statistics}
    \begin{tabular}[]{ll}
        \tabletopline{}%
        Component  & Component in use                                   \\
        \tablemiddleline{}%
        CPU         & One dual core 2.40GHz Intel\textregistered{}
                        Core\texttrademark{}2 CPU,                      \\
                    & with 32KB L1 cache and 4MB L2 cache.              \\
        RAM         & 2GB 667 MHz DDR RAM\@.                            \\
        Hard disk   & One Seagate Barracuda 7200 RPM 250GB SATA disk.   \\
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@

\begin{table}[htbp]
    \caption{Number of rules per Postfix component}
    \empty{}\label{Number of rules per Postfix component}
    \centering{}
    \begin{tabular}{lr}
        \tabletopline{}%
        Postfix component & Number of rules \\
        \tablemiddleline{}%
        \input{build/include-number-of-rules-per-program}
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@

\Graphref{Parsing time relative to shuffled ordering graph} shows the
parsing times of optimal and reverse orderings relative to shuffled
ordering; the mean relative parsing times for different groupings of log
files are given in \tableref{Parsing time relative to shuffled ordering
table}.  This optimisation provides a mean reduction in parsing time of
\input{build/include-optimal-ordering-parsing-time-reduction-other-logs}\%
with normal log files,
\input{build/include-optimal-ordering-parsing-time-reduction-logs-22-62-68}\%
when a mail loop occurs and the distribution of log lines is unusual.
Optimal rule ordering has other benefits, described in
\sectionref{scalability as the number of rules rises}.  Differences in rule
ordering have less effect on parsing time when parsing log files 22 and
62--68, due to the different distribution of log lines in those log files.

@@

XXX WRITE ABOUT PERFECT RULE ORDERING\@; DUNNO WHETHER TO PUT IT IN WITH
RULE ORDERING FOR EFFICIENCY, OR IN ITS OWN SECTION\@.

XXX ADD A TABLE SHOWING PERFECT WORST RELATIVE TO PERFECT BEST\@.

\showgraph{build/graph-perfect-best-and-perfect-worst-and-optimal-and-reverse-vs-shuffled}{Parsing
time including perfect best and worst relative to shuffled
ordering}{Parsing time relative to shuffled ordering including perfect best
and worst graph}

\showtable{build/include-perfect-best-and-optimal-and-reverse-and-perfect-worst-vs-shuffle}{Parsing
time including perfect best and worst relative to shuffled
ordering}{Parsing time including perfect best and worst relative to
shuffled ordering table}

% XXX \FloatBarrier{} MIGHT BE USEFUL TO CONTROL WHERE FLOATS ARE PLACED.

>>>>

\begin{table}[thbp]
    \caption{Details of the computer used to generate statistics}
    \empty{}\label{Details of the computer used to generate statistics}
    \begin{tabular}[]{ll}
        \tabletopline{}%
        Component  & Component in use                                   \\
        \tablemiddleline{}%
        CPU         & One dual core 2.40GHz Intel\textregistered{}
                        Core\texttrademark{}2 CPU,                      \\
                    & with 32KB L1 cache and 4MB L2 cache.              \\
        RAM         & 2GB 667 MHz DDR RAM\@.                            \\
        Hard disk   & One Seagate Barracuda 7200 RPM 250GB SATA disk.   \\
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@

\begin{table}[thbp]
    \caption{Number of rules per Postfix component}
    \empty{}\label{Number of rules per Postfix component}
    \centering{}
    \begin{tabular}{lr}
        \tabletopline{}%
        Postfix component & Number of rules \\
        \tablemiddleline{}%
        \input{build/include-number-of-rules-per-program}
        \tablebottomline{}%
    \end{tabular}
\end{table}

@@

\Graphref{Parsing time relative to shuffled ordering graph} shows the
parsing times of optimal and reverse orderings relative to shuffled
ordering; the mean relative parsing times for different groupings of log
files are given in \tableref{Parsing time relative to shuffled ordering
table}.  This optimisation provides a mean reduction in parsing time of
\input{build/include-optimal-ordering-parsing-time-reduction-other-logs}\%
with normal log files,
\input{build/include-optimal-ordering-parsing-time-reduction-logs-22-62-68}\%
when a mail loop occurs and the distribution of log lines is unusual.
Optimal rule ordering has other benefits, described in
\sectionref{scalability as the number of rules rises}.  \Tableref{Parsing
time relative to shuffled ordering table} shows that differences in rule
ordering have less effect on parsing time when parsing log files 22 and
62--68, due to the different distribution of log lines in those log files.

@@

XXX WRITE ABOUT PERFECT RULE ORDERING\@.

Optimal rule ordering, as described in \sectionref{rule ordering for
efficiency}, is the best rule ordering it is possible to achieve without
having an oracle that magically divines which rule should be used to
recognise each log line.  Such an oracle would give perfect performance,
because only one rule needs to be used to recognise each log line.
\parsername{} can save a list showing which rule recognised each log line,
and use that list to simulate having an oracle and improve parsing speed
the second time a log file is parsed.   This does not provide a practical
benefit, but it does provide a means to evaluate the performance of optimal
rule ordering in comparison to an oracle.  The knowledge can also be used
to generate a perfect worst oracle, where every rule (subject to rule
conditions) is used before the correct rule.

\Graphref{Parsing time relative to shuffled ordering including perfect best
and worst graph} shows the parsing times of the perfect best oracle and
perfect worst oracle relative to shuffled ordering, in addition to the
parsing times of optimal and reverse orderings.  As expected, the perfect
best oracle is more efficient than optimal ordering, and likewise the
perfect worst oracle is less efficient than reverse ordering.

XXX REFER TO SECOND AND THIRD GRAPHS, AND ADD TABLES SHOWING MEAN AND
STDDEV FOR THE THREE GROUPS OF LOGS FILES\@.

XXX WRITE SOMETHING TO MAKE IT EASIER TO GENERATE MEAN AND STDDEV FOR THREE
GROUPS OF LOG FILES\@.

\Graphref{Parsing time of perfect best oracle relative to optimal ordering}

\showgraph{build/graph-perfect-best-and-perfect-worst-and-optimal-and-reverse-vs-shuffled}{Parsing
times relative to shuffled ordering}{Parsing time relative to shuffled
ordering including perfect best and worst graph}

\showgraph{build/graph-perfect-best-vs-optimal}{Parsing time of perfect
best oracle relative to optimal ordering}{Parsing time of perfect best
oracle relative to optimal ordering}

\showgraph{build/graph-perfect-worst-vs-reverse}{Parsing time of perfect
worst oracle relative to reverse ordering}{Parsing time of perfect worst
oracle relative to reverse ordering}

\showtable{build/include-perfect-best-and-optimal-and-reverse-and-perfect-worst-vs-shuffle}{Parsing
time including perfect best and worst oracles relative to shuffled
ordering}{Parsing time including perfect best and worst oracles relative to
shuffled ordering table}
